### 2012-06-13 inst/examples/Reed.Rmd
adding plots of policy function and value function

``` {r  profit}
profit <- profit_harvest(price=1, c0 = 0.0001) 
````

@@

``` {r  grid}
x_grid <- seq(0, 2 * K, length = 100)  
h_grid <- x_grid  
````

@@

We can take a look at the policy function,

``` {r }
qplot(x_grid, x_grid[opt$D[,1]], xlab="stock size", ylab="harvest")
````

Note that this corresponds to constant optimal escapement, 
``` {r }
qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
````

>>>>

``` {r  profit}
profit <- profit_harvest(price=1, c0 = 0.01) 
````

@@

``` {r  grid}
x_grid <- seq(0, 1.5 * K, length = 100)  
h_grid <- x_grid  
````

@@

Plot the policy function (in terms of escapement, `x-h`, rather than harvest `h`) at equilibrium (first time-step):

``` {r policyfn_plot}
qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
````

and the value function (at equilibrium):

``` {r valuefn_plot}
qplot(x_grid, opt$V, xlab="stock size", ylab="value")
````

### 2012-06-13 inst/examples/Sethi.Rmd
adding plots of policy function and value function

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, refresh=2 or`

@@

>>>>

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`

@@

Plot the policy function:

``` {r policyfn_plot}
qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
````

and the value function:

``` {r valuefn_plot}
qplot(x_grid, opt$V, xlab="stock size", ylab="value")
````
